\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{subfigure}
\usepackage[numbers]{natbib}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}

%\usepackage{ulem}
\usepackage{url}
\usepackage{tabu}
\usepackage{booktabs}
\usepackage[numbers]{natbib}
\citestyle{IEEEtran}
\bibliographystyle{IEEEtranN}

%\setlength{\parskip}{0.5em}
\usetikzlibrary{math}
\usetikzlibrary{snakes}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{patterns}
\usetikzlibrary{shapes,arrows,chains}
\usepgfplotslibrary{patchplots,colormaps}
\usetikzlibrary{calc}
\usetikzlibrary{positioning, fit}
\usetikzlibrary{backgrounds}
\usetikzlibrary{intersections}
%\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
%    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Anonymous Accounts Identification via Transaction Graph Analysis*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

%\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%\and
%\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address}
%}

\maketitle

\begin{abstract}
  \textcolor{blue}{
Anonymity, as the born feature of blockchain, let users can perform actions
  underneath public-keys only.
Although different identities hide behind those public-keys, people need
  deanonymize such identities for various
  reasons, like trading,
  making laws, or financial securities.
  However,
  smart contracts, which is
  regarded as the core technology of the future blockchain, make users'
  anonymous actions arbitrary. As a result, new transaction types, new user
  behaviours, and correspondingly new identities emerges in blockchain. And
  existing graph analysis technologies, like clustering, centrality analysis or
  graph partitioning, are helpless to infer identities from the arbitrariness.
}

  \textcolor{blue}{
  In this paper, we propose graph deep learning approach to address the
  arbitrariness. Relying only on the transaction graph structure, our approach shows effectiveness in the evaluation through real date set.
}

  In cryptocurrencies, such as Bitcoin and Ethereum, anonymity is a key feature, which realizing privacy protection by mapping users' identity to public-keys only. On the other hand, deanonymization is equally important since it helps people have better understanding what is occurring on the ecosystem. Challenges are accompanied by the emerging of smart contract. It is hard to infer identity behind account without expert knowledge or external information. In this paper, we propose graph deep learning approach to address the challenges of deanonymization. Relying only on the transaction graph structure, our approach shows effectiveness in the evaluation through real date set.
\end{abstract}

\begin{IEEEkeywords}
Cryptocurrency, Blockchain, Deanonymization, Graph deep learning
\end{IEEEkeywords}

\input{intro.tex}
%\input{background.tex}
\input{analysis.tex}
\input{graph.tex}
\input{model.tex}
\input{experiment.tex}
\input{relatedworks.tex}
\input{conclusion.tex}

\bibliography{reference}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
